### 2011-07-18 docs/visualization/visualization.tex
typo
typos

\renewcommand{\arraystretch}{1.3}

\begin{center}
\begin{longtable}{|l|p{2.25in}|p{2.5in}|}
\caption{Plotfile quantities}
\label{vis:table:plotfile} \\
%
\hline \multicolumn{1}{|c|}{\textbf{plotfile variable name}} & 
       \multicolumn{1}{|c|}{\textbf{description}} & 
       \multicolumn{1}{|c|}{\textbf{runtime parameter controlling output}} \\ \hline
\endfirsthead

@@

{\tt z\_vel}   & $\wt$  & 3-d runs online \\

@@

{\tt rhoh}   & $(\rho h)$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt h}      & $(\rho h)/\rho$   & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt rhohpert}          & $(\rho h) - (\rho h)_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt tfromh}            & $T(\rho, h, X_k)$    & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt deltaT}            & $[T(\rho, h, X_k) - T(\rho, p_0, X_k)]/T(\rho, h, X_k)$  & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt deltap}            & $|p(\rho,h,X_k) - p_0|/p_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

>>>>

\renewcommand{\arraystretch}{1.3}
{\footnotesize
\begin{center}
\begin{longtable}{|l|p{2.25in}|p{2.5in}|}

\caption{Plotfile quantities}
\label{vis:table:plotfile} \\
%
\hline \multicolumn{1}{|c|}{\textbf{plotfile variable name}} & 
       \multicolumn{1}{|c|}{\textbf{description}} & 
       \multicolumn{1}{|c|}{\textbf{runtime parameter controlling output}} \\ \hline
\endfirsthead

@@

{\tt z\_vel}   & $\wt$  & 3-d runs only \\

@@

{\tt rhoh}   & $(\rho h)$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt h}      & $(\rho h)/\rho$   & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt rhohpert}          & $(\rho h) - (\rho h)_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt tfromh}            & $T(\rho, h, X_k)$    & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt deltaT}            & $[T(\rho, h, X_k) - T(\rho, p_0, X_k)]/T(\rho, h, X_k)$  & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

{\tt deltap}            & $|p(\rho,h,X_k) - p_0|/p_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} and {\tt plot\_h\_with\_use\_tfromp = T}) \\           

@@

}
